---
title: "Using the `powers` package"
author: "Tanvi Mittal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! 

```{r}
library(powers)
suppressPackageStartupMessages(library(tidyverse))
library(knitr)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, 1.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
lapply(my_list,function(x) x^(1/3))
## Use powers instead!
lapply(my_list, square)
lapply(my_list,cbrt)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
cbrt(1:10,plot_it=TRUE)
```

Wow!!!

Power package also consists of function for Box-cox transformation. Box-cox transformation is used to normalize the data by varying lambda(exponent) between -5 to 5.

Example to use the function:

```{r}
kable(tibble(input=1:10,BCtransformed_output = box.cox(1:10,2)))
```

